Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-08-17 DGMM2025/visibility.tex
p1 corrections camera ready
p2 corrections camera ready

    All the theory and algorithms presented in this section are
    defined and valid in arbitrary dimension $d$. They will however be
    illustrated in 2d for clarity, while experiments willl be
    performed on 3d digital shapes.  Let $\Z^d$ be the $d$-dimensional
    digital space.  Let $\mathcal{C}^d$ be the (cubical) cell complex
    induced by the lattice $\Z^d$ : its 0-cells are the points of
    $\Z^d$, its 1-cells are the open unit segments joining two 0-cells
    at distance 1, its 2-cells are the open unit squares, \ldots, and
    its $d$-cells are the $d$-dimensional open unit hypercubes with
    vertices in $\Z^d$.  We denote by $\mathcal{C}^d_k$ the set of its
    $k$-cells, for $0 \Le k \Le d$.  In the following, a cell always
    designates an element of $\mathcal{C}^d$, and the term subcomplex
    always indicates a subset of $\mathcal{C}^d$.

@@

    % Examples of visibility in 2D
    \begin{figure}[t]
      \centering
      \input{visibility.tikz}
      \caption{Examples of visibility and non visibility in 2D within
        the set $X$ (represented with black disks $\bullet$).}
      \label{fig:visibility-2d}
    \end{figure}

>>>>

    All the theory and algorithms presented in this section are
    defined and valid in arbitrary dimension $d$. They will however be
    illustrated in 2d for clarity, while experiments will be
    performed on 3d digital shapes.  Let $\Z^d$ be the $d$-dimensional
    digital space.  Let $\mathcal{C}^d$ be the (cubical) cell complex
    induced by the lattice $\Z^d$ : its 0-cells are the points of
    $\Z^d$, its 1-cells are the open unit segments joining two 0-cells
    at distance 1, its 2-cells are the open unit squares, \ldots, and
    its $d$-cells are the $d$-dimensional open unit hypercubes with
    vertices in $\Z^d$.  We denote by $\mathcal{C}^d_k$ the set of its
    $k$-cells, for $0 \Le k \Le d$.  In the following, a cell always
    designates an element of $\mathcal{C}^d$, and the term subcomplex
    always indicates a subset of $\mathcal{C}^d$.

@@

    % Examples of visibility in 2D
    \begin{figure}[t]
      \centering
      \input{visibility.tikz}
      \caption{Examples of visibility and non visibility in 2D within
        the set $X$ (represented with black dots $\bullet$).}
      \label{fig:visibility-2d}
    \end{figure}
